Preprocessing

### 2023-09-07 analysis/preprocessing.Rmd
Added columns: cope, field, jif
Also added additional variations of 'commentaries' and 'letters' chunk ~507

```{r}
d_journals <- d_journals %>%
  select(timestamps = Timestamp,
         sample_id,
         coder_id = `Coder's Initials`,
         journal = `Journal Name`,
         journal_empirical = `Does the journal publish empirical research?`,
         anyPPC = `Check the article types page and check for web comments — does the journal offer any type of PPC?`,
         A_ppc_name = `A. Enter the name of the PPC type offered by the journal:`,
         B_ppc_name = `B. Enter the name of the PPC type offered by the journal:`,
         C_ppc_name = `C. Enter the name of the PPC type offered by the journal:`,
         A_ppc_description = `A. Enter the verbatim description of this type of PPC provided by the journal`,
         B_ppc_description = `B. Enter the verbatim description of this type of PPC provided by the journal`,
         C_ppc_description = `C. Enter the verbatim description of this type of PPC provided by the journal`,
         A_ppc_length = `A. Are there any length limits for this type of PPC?`,
         B_ppc_length = `B. Are there any length limits for this type of PPC?`,
         C_ppc_length = `C. Are there any length limits for this type of PPC?`,
         A_ppc_time = `A. Are there any time limits for submission of this type of PPC?`,
         B_ppc_time = `B. Are there any time limits for submission of this type of PPC?`,
         C_ppc_time = `C. Are there any time limits for submission of this type of PPC?`,
         A_ppc_ref = `A. Are there any reference limits for this type of PPC?`,
         B_ppc_ref = `B. Are there any reference limits for this type of PPC?`,
         C_ppc_ref = `C. Are there any reference limits for this type of PPC?`,
         A_ppc_review = `A. Is this type of PPC sent for independent external peer review?`,
         B_ppc_review = `B. Is this type of PPC sent for independent external peer review?`,
         C_ppc_review = `C. Is this type of PPC sent for independent external peer review?`,
         A_ppc_note = `A. Anything additional, unusual, or interesting to note?`,
         B_ppc_note = `B. Anything additional, unusual, or interesting to note?`,
         C_ppc_note = `C. Anything additional, unusual, or interesting to note?`,
         general_note = `Anything additional, unusual, or interesting to note?`,
         -starts_with("D. "),
         -ends_with("Are there any other types of PPC in this journal? (Remember to check for web comments!)`"))

@@

d_journals %>%
  group_by(journal) %>%
  mutate(has_final = any(coder_id == "FINAL (TEH)")) %>%
  filter(has_final == F) %>% View()

@@

```{r}
d_journals <- d_journals %>%
  pivot_longer( # pivot to long format
    cols = c(-journal,-journal_empirical,-sample_id,-anyPPC,-general_note),
    names_to = c("PPC_type", ".value"), 
    names_sep = "_ppc_"
  )
```

@@

```{r}
commentaries <- c("Brief comment", "Brief Comment", "commentaries", "Commentaries", "Commentary", "Comments", "Matters Arising", "Observations & Commentaries", "Open peer commentaries", "Short Communications and Commentaries", "Short Research Notes", "Text review")
letters <- c("Letter", "Letters", "Letter to the editor", "Letters to the editor", "letters to the editor", "Letters to the Editor.", "letters to the editors", "Letters to the Editors")
# web_comments <- c()
other <- c("Verification reports")
```

```{r}
d_journals <- d_journals %>%
  mutate(name_harmonized = case_when(
    name %in% commentaries ~ "Commentary",
    name %in% letters ~ "Letters",
    name %in% other ~ "Other"
  ))
```
# Reclassify and reformat

@@

```{r}
d_journals <- d_journals %>%
  mutate(sample_id = factor(sample_id),
         journal_name = factor(journal),
         is_empirical = as.logical(fct_recode(journal_empirical, T = "Yes", F = "No")),
         has_ppc = fct_recode(anyPPC, 
                             "ARCHIVE" = "ARCHIVE ONLY", 
                             "NO IMPLICIT" = "NO (there are no PPC options)",
                             "NO EXPLICIT" = "NO (explicit statement that PPC is not accepted)")) %>%
  select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized)
```

>>>>

```{r}
d_journals <- d_journals %>%
  select(timestamps = Timestamp,
         sample_id,
         coder_id = `Coder's Initials`,
         journal = `Journal Name`,
         journal_empirical = `Does the journal publish empirical research?`,
         anyPPC = `Check the article types page and check for web comments — does the journal offer any type of PPC?`,
         A_ppc_name = `A. Enter the name of the PPC type offered by the journal:`,
         B_ppc_name = `B. Enter the name of the PPC type offered by the journal:`,
         C_ppc_name = `C. Enter the name of the PPC type offered by the journal:`,
         A_ppc_description = `A. Enter the verbatim description of this type of PPC provided by the journal`,
         B_ppc_description = `B. Enter the verbatim description of this type of PPC provided by the journal`,
         C_ppc_description = `C. Enter the verbatim description of this type of PPC provided by the journal`,
         A_ppc_length = `A. Are there any length limits for this type of PPC?`,
         B_ppc_length = `B. Are there any length limits for this type of PPC?`,
         C_ppc_length = `C. Are there any length limits for this type of PPC?`,
         A_ppc_time = `A. Are there any time limits for submission of this type of PPC?`,
         B_ppc_time = `B. Are there any time limits for submission of this type of PPC?`,
         C_ppc_time = `C. Are there any time limits for submission of this type of PPC?`,
         A_ppc_ref = `A. Are there any reference limits for this type of PPC?`,
         B_ppc_ref = `B. Are there any reference limits for this type of PPC?`,
         C_ppc_ref = `C. Are there any reference limits for this type of PPC?`,
         A_ppc_review = `A. Is this type of PPC sent for independent external peer review?`,
         B_ppc_review = `B. Is this type of PPC sent for independent external peer review?`,
         C_ppc_review = `C. Is this type of PPC sent for independent external peer review?`,
         A_ppc_note = `A. Anything additional, unusual, or interesting to note?`,
         B_ppc_note = `B. Anything additional, unusual, or interesting to note?`,
         C_ppc_note = `C. Anything additional, unusual, or interesting to note?`,
         general_note = `Anything additional, unusual, or interesting to note?`,
         cope, field, jif,
         -starts_with("D. "),
         -ends_with("Are there any other types of PPC in this journal? (Remember to check for web comments!)`"))

@@

@@

```{r}
d_journals <- d_journals %>%
  pivot_longer( # pivot to long format
    cols = c(-journal,-journal_empirical, -sample_id,-anyPPC,-general_note, -cope, -field, -jif),
    names_to = c("PPC_type", ".value"), 
    names_sep = "_ppc_"
  )
```

@@

```{r}
commentaries <- c("Brief comment", "Brief Comment", "Brief empirical notes", "brief peer commentaries or rebuttals", "commentaries", "Commentaries", "Commentary", "Comments", "Commentry", "commentary", "Commentary articles", "Matters Arising", "Observations & Commentaries", "Open peer commentaries", "Short Communications and Commentaries", "Short Research Notes", "Text review")
letters <- c("Letter", "Letters", "Letter to the editor", "Letters to the editor", "letters to the editor", "Letters to the Editor.", "letters to the editors", "Letters to the Editors", "Letters to the Editor", "Letter to the Editor")
# web_comments <- c()
other <- c("Verification reports")
```

```{r}
d_journals <- d_journals %>%
  mutate(name_harmonized = case_when(
    name %in% commentaries ~ "Commentary",
    name %in% letters ~ "Letters",
    name %in% other ~ "Other"
  ))
```

# Reclassify and reformat

@@

```{r}
d_journals <- d_journals %>%
  mutate(sample_id = factor(sample_id),
         journal_name = factor(journal),
         is_empirical = as.logical(fct_recode(journal_empirical, T = "Yes", F = "No")),
         has_ppc = fct_recode(anyPPC, 
                             "ARCHIVE" = "ARCHIVE ONLY", 
                             "NO IMPLICIT" = "NO (there are no PPC options)",
                             "NO EXPLICIT" = "NO (explicit statement that PPC is not accepted)")) %>%
  select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized, cope, field, jif)
```
